More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
Proof improvement
Proof Lemma 4 completed

-\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact
the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (2) we directly conclude 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction
Suppose
$
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) $

By recurrence hypothesis the theorem is \True for any set of transitions of length $l$. In particular, we have

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \implies  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

We need to prove the same implication with

 by adding the transition:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}

First by using rule (2) we can directly conclude :
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

By rule (1) we have
${ \openrule
         {
          \emptyset,\True,\Id(s')
				 } {s' \OTWeakarrow {\tau} s'} \in \WT
}$
Finally by using rule (3) we compose the three rules:

\TODO{todo}

The right part of the disjunction, i.e.
\begin{mathpar}
\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
\end{mathpar}
is handled trivially by rule (WT1)

\end{itemize}
\TODO{add rule numbers WT1 WT2 WT3, and refer to them}

@@

\begin{itemize}
\item case rule (WT1):
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTarrow {\tau} s} \in \mathcal{T}
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.

\item case rule (WT2). \TODO{write inference}
\begin{mathpar}
\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
\end{mathpar}

This proves the implication with $n=0$ and $m=0$.

\item case rule (WT3).
\TODO{put WT3 here}

%
%
%Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
%
%\begin{mathpar}
%{ \openrule
%         {
%           \overline{\gamma}\!,\Pred,\Post
%				 } {s \OTWeakarrow {\alpha} s'} \in \WT
%}
%\end{mathpar}
%We have two cases:
%\begin{itemize}
\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \True$ and $\Post=\Id(s)$. So by rule (2) we have:

\item Otherwise, by rule (2) we conclude that we have:

where $\overline{\gamma} = \vis{\overline{\beta}}$
\end{itemize}
\item Step: by using rule (3) we can rewrite a weak transition:

\begin{mathpar}
{ \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar}

as

\begin{mathpar}
\inferrule{
\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
\quad
\openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3 }
         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
%\\
%\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}{}
\end{mathpar}

such that \\
$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$, 
$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post=$ \TODO{Voir comment l'exprimer}\\

@@

\item By induction hypothesis and simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where 
\begin{mathpar} 
s=s^1_0 \wedge\, s^1_{n_1}=s_1 \quad
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
\quad
\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
\end{mathpar}

\item and
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where
\begin{mathpar} 
s_2=s^3_0 \wedge s^1_{m_1}=s'\quad
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}}\quad
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i \quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
\end{mathpar}

\item and 
\begin{mathpar}
\bigg(\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
\end{mathpar}
\end{enumerate}

Therefore, we can conclude that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

@@

where\\
\begin{mathpar} 
s_1=s^1_0 \wedge s^1_{n_1+n_2}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}=s'\\
\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
\dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
\end{mathpar}

>>>>

\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:

@@

\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact
the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
\begin{itemize}
\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule (\WTDeux) we directly conclude 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.   Induction step is to infer that formula holds for transitions of length $l + 1$. As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
\begin{mathpar}
\Bigg(\forall i \in [0\ldots n+1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
\end{mathpar}

By recurrence hypothesis the theorem is \True~ for any set of transitions of length $l$. In particular, we have

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \implies  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
}
\end{mathpar}

We need to prove the same implication with  by adding the transition:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
%}
\end{mathpar}
It will remain so. First by using rule (\WTDeux) we can directly conclude :
\begin{mathpar}

 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\tau} s'} \in \mathcal{T}
\implies 
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\tau} s'} \in \WT
}
\end{mathpar}

On the other hand, by rule (\WTUn) we have
\begin{mathpar}
 \openrule
         {
          \emptyset,\True,\Id(s')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\end{mathpar}

Finally by using rule (\WTTrois) we compose the three weak transitions:

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \vis{\overline{\beta}},\Pred,\Post   }
         {s \OTWeakarrow {\tau} s'} \in \WT
\qquad
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
\qquad
\openrule
         {
          \emptyset,\True,\Id(s')
				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
          \vis{\overline{\beta}} \dotcup \overline{\gamma},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s''} \in\WT
} \WTTrois
\end{mathpar}

The right part of the disjunction, i.e.
\begin{mathpar}
\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
\end{mathpar}
is handled trivially by rule (\WTUn)

\end{itemize}

@@

\begin{itemize}
\item Case rule (\WTUn):
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTWeakarrow {\tau} s} \in \WT
} \implies \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
\end{mathpar}

\item Case rule (\WTDeux):
\begin{mathpar}
\openrule
         {
           \overline{\gamma},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'} \in \WT \implies
         \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTWeakarrow {\alpha} s'} \in \mathcal{T}         
\end{mathpar}
where $\overline{\gamma} = \vis{\overline{\beta}}$.
These two cases prove the implication with $n=0$ and $m=0$.

\item Case rule (\WTTrois):
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

%where 
%$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$,
%$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post= ({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K}$

@@

\item By induction hypothesis this means each tau weak transition can be written as a series of tau transitions, hence by simplification we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

\item Similarly, we have: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where\\
$
s_2=s^3_0 \wedge s^1_{m_1}=s',
\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
$

\item On the other hand, by induction hypothesis we have:
\begin{mathpar}
\bigg(\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
$
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
$
\end{enumerate}
~~\\

Therefore, we can deduce that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

@@

where\\
$
s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s',
\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
\dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta^3_i}}
\\
\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
$

\end{itemize}
